### 2016-05-04 paper/paper-template-latex/paper_template.tex

\documentclass[conference]{IEEEtran}
\usepackage{times}

% numbers option provides compact numerical references in the text.
\usepackage[numbers]{natbib}
\usepackage{multicol}
\usepackage[bookmarks=true]{hyperref}

\pdfinfo{
   /Author (Anonymous)
   /Title  (Extended Abstract: Grounding Language to Reward Functions with Abstract Markov Decision Processes)
   /CreationDate (D:20160503120000)
   /Subject (AMDPs, Robots, Language)
   /Keywords (Grounded Language; AMDP)
}

\begin{document}

% paper title
\title{Extended Abstract: Grounding Language to Reward Functions With Abstract Markov Decision Processes}

% You will get a Paper-ID when submitting a pdf file to the conference system
\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}

%\author{\authorblockN{Michael Shell}
%\authorblockA{School of Electrical and\\Computer Engineering\\
%Georgia Institute of Technology\\
%Atlanta, Georgia 30332--0250\\
%Email: mshell@ece.gatech.edu}
%\and
%\authorblockN{Homer Simpson}
%\authorblockA{Twentieth Century Fox\\
%Springfield, USA\\
%Email: homer@thesimpsons.com}
%\and
%\authorblockN{James Kirk\\ and Montgomery Scott}
%\authorblockA{Starfleet Academy\\
%San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212\\
%Fax: (888) 555--1212}}

% avoiding spaces at the end of the author lines is not a problem with
% conference papers because we don't use \thanks or \IEEEmembership

% for over three affiliations, or if they all won't fit within the width
% of the page, use this alternative format:
%
%\author{\authorblockN{Michael Shell\authorrefmark{1},
%Homer Simpson\authorrefmark{2},
%James Kirk\authorrefmark{3},
%Montgomery Scott\authorrefmark{3} and
%Eldon Tyrell\authorrefmark{4}}
%\authorblockA{\authorrefmark{1}School of Electrical and Computer Engineering\\
%Georgia Institute of Technology,
%Atlanta, Georgia 30332--0250\\ Email: mshell@ece.gatech.edu}
%\authorblockA{\authorrefmark{2}Twentieth Century Fox, Springfield, USA\\
%Email: homer@thesimpsons.com}
%\authorblockA{\authorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
%Telephone: (800) 555--1212, Fax: (888) 555--1212}
%\authorblockA{\authorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}

\maketitle

\begin{abstract}
The abstract goes here.
\end{abstract}

\IEEEpeerreviewmaketitle

\section{Introduction}
The issue of abstraction is key to the field of reinforcement learning as it represents a logical way to accelerate planning time within sequential decision making problems by breaking apart large, complex tasks into smaller sub-tasks. Most often, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism for reinforcement learning. Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or simply pruning irrelevant states from consideration. Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``action''. Unfortunately, many of these methods fall short in that they simply add more elements to either the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.

Our approach in tackling this problem of abstraction is to utilize abstract Markov decision processes (AMDPs) which represent a decomposition of a regular MDPs creating multiple layers of abstraction. To briefly summarize, MDPs are represented by the five-tuple: $\langle$ ${\cal S}$, ${\cal A}$, ${\cal T}$, ${\cal R}$, $\gamma$ $\rangle$, where ${\cal S}$ is a set of states of the world; ${\cal A}$ is a set of actions that the agent can take; ${\cal T}$ is a function that computes the probability of transitioning from one state to another via applying a specified action; ${\cal R}$ is a function specifying the agent's reward for taking an action within a particular state ; and $\gamma$ is a discount factor. AMDPs take on a slightly different form by maintaining a stack of internal MDPs, each of which represents a different layer of abstraction for the input problem. The base level MDP represents the original task as it was given, while higher level MDPs are hard coded over abstracted state and action spaces (with corresponding transition dynamics and reward functions). These higher level MDPs capture the notion of sub-goals within the problem and so whenever the agent in a lower level need take an action, the current state information is fed upward to the next highest level of the AMDP. Once the highest MDP is reached, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level which is then stored and reused so as to avoid redundant computation. Surjective state mappings are maintained from higher to lower level MDPs allowing for a backpropagation to occur once a higher level sub-task has been solved and this process then repeats onnce the backpropagation returns all the way down to the base level MDP. It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs.

In order to examine the effectiveness of the abstraction imposed by AMDPs, we extend prior work by MacGlashan et.al. on grounding natural language commands to the reward function of an MDP~\cite{MacGlashan2015GroundingEC}. In particular, we take an AMDP and evaluate the effectiveness of grounding a reward function at each level of the AMDP using natural language commands taken individually from each level of abstraction. In the context of the cleanup world domain used by MacGlashan et.al., this corresponds to an AMDP with three layers of abstraction: high, mid, and low.

We take a natural language command from an arbitrary level and apply IBM Model II translation to ground it to a reward function for each level of the AMDP.

We show that grounding an arbitrary natural language command to a reward function will be most successful when the natural language command and MDP correspond to the same level of abstraction. For the purpose of staying consistent with the experimental method used by MacGlashan et.al., we will leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within BURLAP to conduct experiments and collect results.

\section{Section}

Section text here.

\subsection{Subsection Heading Here}
Subsection text here.

\subsubsection{Subsubsection Heading Here}
Subsubsection text here.

\section{RSS citations}

Please make sure to include \verb!natbib.sty! and to use the
\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
citation commands, most usefully \verb!\citet!. For example, rather than the
awkward construction

{\small
\begin{verbatim}
\cite{kalman1960new} demonstrated...
\end{verbatim}
}

\noindent
rendered as ``\cite{kalman1960new} demonstrated...,''
or the
inconvenient

{\small
\begin{verbatim}
Kalman \cite{kalman1960new}
demonstrated...
\end{verbatim}
}

\noindent
rendered as
``Kalman \cite{kalman1960new} demonstrated...'',
one can
write

{\small
\begin{verbatim}
\citet{kalman1960new} demonstrated...
\end{verbatim}
}
\noindent
which renders as ``\citet{kalman1960new} demonstrated...'' and is
both easy to write and much easier to read.

\subsection{RSS Hyperlinks}

This year, we would like to use the ability of PDF viewers to interpret
hyperlinks, specifically to allow each reference in the bibliography to be a
link to an online version of the reference.
As an example, if you were to cite ``Passive Dynamic Walking''
\cite{McGeer01041990}, the entry in the bibtex would read:

{\small
\begin{verbatim}
@article{McGeer01041990,
  author = {McGeer, Tad},
  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}},
  volume = {9},
  number = {2},
  pages = {62-82},
  year = {1990},
  doi = {10.1177/027836499000900206},
  URL = {http://ijr.sagepub.com/content/9/2/62.abstract},
  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html},
  journal = {The International Journal of Robotics Research}
}
\end{verbatim}
}
\noindent
and the entry in the compiled PDF would look like:

\def\tmplabel#1{[#1]}

\begin{enumerate}
\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
1990.
\end{enumerate}
%
where the title of the article is a link that takes you to the article on IJRR's website.

Linking cited articles will not always be possible, especially for
older articles. There are also often several versions of papers
online: authors are free to decide what to use as the link destination
yet we strongly encourage to link to archival or publisher sites
(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
the extent possible.

\section{Conclusion}
\label{sec:conclusion}

The conclusion goes here.

\section*{Acknowledgments}

%% Use plainnat to work nicely with natbib.

\bibliographystyle{plainnat}
\bibliography{references}

\end{document}

### 2016-05-04 src/commands/amdp/tools/CleanupDriverTest.java
Testing L1L0 episode analysis

@@ -41,7 +41,7 @@ public class CleanupDriverTest {
 
             State s = CleanupWorld.getExperimentState(domain);
 
-            GroundedProp groundedProp = new GroundedProp(domain.getPropFunction(CleanupWorld.PF_BLOCK_IN_ROOM),  new String[]{"block0", "room0"});
+            GroundedProp groundedProp = new GroundedProp(domain.getPropFunction(CleanupWorld.PF_AGENT_IN_ROOM),  new String[]{"agent0", "room0"});
 
 
             StateConditionTest sc = new CleanupL1AMDPDomain.GroundedPropSC(groundedProp);
@@ -69,6 +69,8 @@ public class CleanupDriverTest {
 
             System.out.println(ea.stateSequence);
             System.out.println(ea.actionSequence);
+            String prefix = "data/amdpData/L1L0/ea/";
+            ea.writeToFile(prefix + "go|to|red|door|go|into|red|room");
 
             //		System.out.println(ea.getState(0).toString());
             System.out.println("total actions:" + ea.actionSequence.size());

### 2016-05-05 src/commands/amdp/tools/CleanupDriverTest.java
First draft of paper complete

@@ -2,7 +2,6 @@ package commands.amdp.tools;
 
 import burlap.behavior.policy.Policy;
 import burlap.behavior.singleagent.EpisodeAnalysis;
-import burlap.behavior.singleagent.auxiliary.EpisodeSequenceVisualizer;
 import burlap.behavior.singleagent.planning.stochastic.rtdp.BoundedRTDP;
 import burlap.behavior.valuefunction.ValueFunctionInitialization;
 import burlap.oomdp.auxiliary.common.GoalConditionTF;
@@ -13,11 +12,11 @@ import burlap.oomdp.core.states.State;
 import burlap.oomdp.singleagent.RewardFunction;
 import burlap.oomdp.singleagent.common.GoalBasedRF;
 import burlap.oomdp.statehashing.SimpleHashableStateFactory;
-import burlap.oomdp.visualizer.Visualizer;
-import commands.amdp.domain.*;
+import commands.amdp.domain.CleanupDomainDriver;
+import commands.amdp.domain.CleanupL1AMDPDomain;
+import commands.amdp.domain.CleanupWorld;
+import commands.amdp.domain.PullCostGoalRF;
 import commands.amdp.hardcoded.FixedDoorCleanupEnv;
-
-import java.util.Arrays;
 
 /**
  * Created by Dilip Arumugam on 5/4/16.
@@ -25,59 +24,51 @@ import java.util.Arrays;
 public class CleanupDriverTest {
 
     public static void main(String[] args) {
+        double lockProb = 0.0;
 
-        boolean runGroundLevelBoundedRTDP = true;
+        CleanupWorld dgen = new CleanupWorld();
+        dgen.includeDirectionAttribute(true);
+        dgen.includePullAction(false);
+        dgen.includeWallPF_s(true);
+        dgen.includeLockableDoors(true);
+        dgen.setLockProbability(lockProb);
+        Domain domain = dgen.generateDomain();
 
-        if(runGroundLevelBoundedRTDP){
-            double lockProb = 0.0;
+        State s = CleanupWorld.getExperimentState(domain);
 
-            CleanupWorld dgen = new CleanupWorld();
-            dgen.includeDirectionAttribute(true);
-            dgen.includePullAction(false);
-            dgen.includeWallPF_s(true);
-            dgen.includeLockableDoors(true);
-            dgen.setLockProbability(lockProb);
-            Domain domain = dgen.generateDomain();
-
-            State s = CleanupWorld.getExperimentState(domain);
-
[…]

### 2016-05-05 src/commands/amdp/tools/JointGP.java

@@ -1,0 +1,22 @@
+package commands.amdp.tools;
+
+import burlap.oomdp.core.GroundedProp;
+import burlap.oomdp.core.PropositionalFunction;
+import burlap.oomdp.core.states.State;
+
+/**
+ * Created by Dilip Arumugam on 5/4/16.
+ */
+public class JointGP extends GroundedProp {
+
+    public JointGP(PropositionalFunction p, String[] par) {
+        this.pf = p;
+        this.params = par;
+    }
+
+    @Override
+    public boolean isTrue(State s){
+
+    }
+
+}

### 2016-05-05 src/commands/amdp/domain/CleanupDomainDriver.java
Finished collecting L1L0 data

@@ -311,6 +311,9 @@ public class CleanupDomainDriver {
 		else if(PFName.equals(CleanupWorld.PF_BLOCK_IN_DOOR)){
 			return new BlockToRegionHeuristic(params[0], params[1], discount, lockProb);
 		}
+		else if(PFName.equals(CleanupWorld.PF_BLOCK_IN_DOOR + " " + CleanupWorld.PF_AGENT_IN_DOOR)){
+			return new JointHeuristic(new BlockToRegionHeuristic(params[0], params[1], discount, lockProb), new AgentToRegionHeuristic(params[1], discount, lockProb));
+		}
 		throw new RuntimeException("Unknown Reward Function with propositional function " + PFName + ". Cannot construct l0 heuristic.");
 	}
 
@@ -438,6 +441,27 @@ public class CleanupDomainDriver {
 			double v = freeRegion ? fullChanceV : lockProb * fullChanceV + (1. - lockProb)*0.;
 
 			return v;
+		}
+	}
+
+	public static class JointHeuristic implements ValueFunctionInitialization{
+
+		protected final ValueFunctionInitialization h1;
+		protected final ValueFunctionInitialization h2;
+
+		public JointHeuristic(ValueFunctionInitialization h1, ValueFunctionInitialization h2){
+			this.h1 = h1;
+			this.h2 = h2;
+		}
+
+		@Override
+		public double qValue(State state, AbstractGroundedAction abstractGroundedAction) {
+			return h1.value(state) + h2.value(state);
+		}
+
+		@Override
+		public double value(State state) {
+			return h1.value(state) + h2.value(state);
 		}
 	}
 

### 2016-05-05 src/commands/amdp/domain/JointPF.java

@@ -1,0 +1,34 @@
+package commands.amdp.domain;
+
+import burlap.oomdp.core.Domain;
+import burlap.oomdp.core.PropositionalFunction;
+import burlap.oomdp.core.states.State;
+
+import java.util.Arrays;
+import java.util.Collection;
+
+/**
+ * Created by Dilip Arumugam on 5/5/16.
+ */
+public class JointPF extends PropositionalFunction {
+
+    Collection<PropositionalFunction> pfs;
+
+    public JointPF(String name, Domain domain, String[] parameterClasses, Collection<PropositionalFunction> pfs){
+        super(name, domain, parameterClasses);
+        this.pfs = pfs;
+    }
+
+    @Override
+    public boolean isTrue(State state, String... strings) {
+        boolean ret = true;
+        int paramCounter = 0;
+        for(PropositionalFunction pf : pfs){
+            int numParams = pf.getParameterClasses().length;
+            ret &= pf.isTrue(state, Arrays.copyOfRange(strings, paramCounter, paramCounter + numParams));
+            paramCounter += numParams;
+        }
+
+        return ret;
+    }
+}

### 2016-05-05 src/commands/amdp/experiments/cleanupL1/CleanupL1ControllerConstructor.java

@@ -112,7 +112,7 @@ public class CleanupL1ControllerConstructor implements ControllerConstructor{
         labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|go|to|red|door.txt", "agentInRegion(agent0, door0)");
         labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|move|to|green|door|move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
         labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door.txt", "blockInRegion(block0, door0)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|go|to|red|door.txt", "agentInRegion(agent0, door0) blockInRegion(block0, door0)");
+        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|go|to|green|door.txt", "agentInRegion(agent0, door0) blockInRegion(block0, door0)");
         labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|move|to|red|door|move|bag|to|red|room.txt", "blockInRegion(block0, room0)");
         labels.put("go|to|red|door|go|to|blue|room.txt", "agentInRegion(agent0, room2)");
         labels.put("go|to|red|door|go|to|red|room|move|bag|to|green|door.txt", "blockInRegion(block0, door1)");

### 2016-05-05 paper/paper-template-latex/paper_template.tex
Add updated paper

@@
 \section{Introduction}
-The issue of abstraction is key to the field of reinforcement learning as it represents a logical way to accelerate planning time within sequential decision making problems by breaking apart large, complex tasks into smaller sub-tasks.
-Most often, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism for reinforcement learning.
-Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or simply pruning irrelevant states from consideration.
+When dealing with the issue of efficiently solving large-scale sequential decision making problems defined by complex state-action spaces, the ability to identify and leverage multiple layers of abstraction is key.
+Developing good methods of abstraction represents a logical way to accelerate planning time by breaking apart large, complex tasks into smaller sub-tasks.
+Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and achieving sub-goals.
+Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilize multiple layers of abstraction over all components of the Markov Decision Process (MPD) in order to efficiently learn in complex domains.
+In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the abstraction based on the success of these groundings.
+
+\section{Prior Work}
+Typically, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism in the hopes of improving overall problem tractability.
+Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or intelligently pruning states that are irrelevant to the overall task from consideration.
 Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``action''.
-Unfortunately, many of these methods fall short in that they simply add more elements to either the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.
+Unfortunately, these methods suffer from potentially increasing the size of the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.
 
-Our approach in tackling this problem of abstraction is to utilize abstract Markov decision processes (AMDPs) which represent a decomposition of a regular MDPs creating multiple layers of abstraction.
-To briefly summarize, MDPs are represented by the five-tuple: $\langle$ ${\cal S}$, ${\cal A}$, ${\cal T}$, ${\cal R}$, $\gamma$ $\rangle$, where ${\cal S}$ is a set of states of the world; ${\cal A}$ is a set of actions that the agent can take; ${\cal T}$ is a function that computes the probability of transitioning from one state to another via applying a specified action; ${\cal R}$ is a function specifying the agent's reward for taking an action within a particular state ; and $\gamma$ is a discount factor.
-AMDPs take on a slightly different form by maintaining a stack of internal MDPs, each of which represents a different layer of abstraction for the input problem.
-The base level MDP represents the original task as it was given, while higher level MDPs are hard coded over abstracted state and action spaces (with corresponding transition dynamics and reward functions).
-These higher level MDPs capture the notion of sub-goals within the problem and so whenever the agent in a lower level need take an action, the current state information is fed upward to the next highest level of the AMDP.
-Once the highest MDP is reached, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level which is then stored and reused so as to avoid redundant computation.
-Surjective state mappings are maintained from higher to lower level MDPs allowing for a backpropagation to occur once a higher level sub-task has been solved and this process then repeats onnce the backpropagation returns all the way down to the base level MDP.
-It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs.
+\section{Abstract Markov Decision Processes}
 
-In order to examine the effectiveness of the abstraction imposed by AMDPs, we extend prior work by MacGlashan et.al.
-on grounding natural language commands to the reward function of an MDP~\cite{MacGlashan2015GroundingEC}.
-In particular, we take an AMDP and evaluate the effectiveness of grounding a reward function at each level of the AMDP using natural language commands taken individually from each level of abstraction.
-In the context of the cleanup world domain used by MacGlashan et.al., this corresponds to an AMDP with three layers of abstraction: high, mid, and low.
+Our approach in tackling this problem of abstraction is to utilize abstract Markov decision processes (AMDPs) which represent a decomposition of a regular MDP resulting in a tiered hierarchy where each level represents an abstraction over the previous one.
+To briefly summarize, MDPs are represented by a five-tuple: $\langle$ ${\cal S}$, ${\cal A}$, ${\cal T}$, ${\cal R}$, $\gamma$ $\rangle$, where ${\cal S}$ is the set of possible states in the world; ${\cal A}$ is a set of all available actions that can be executed; ${\cal T}$ is a function that computes the probability of transitioning from one state to another by executing an action; ${\cal R}$ is a function specifying the agent's reward for taking an action within a particular state ; and $\gamma$ is a discount factor.
 
-We take a natural language command from an arbitrary level and apply IBM Model II translation to ground it to a reward function for each level of the AMDP.
+Building on top of this, AMDPs take a layered approach by maintaining a stack of MDPs, each of which represents a different layer of abstraction for the input problem.
+The base (lowest) level MDP is always the MDP representing the original problem while higher level MDPs are hard coded over smaller state and action spaces (with corresponding transition dynamics and reward functions).
+Each state and action in a higher level MDP is implemented as an abstraction over multiple states and actions in the lower level creating a many-to-one mapping (as we move up the stack) resulting in smaller, more tractable state-action spaces.
+Intuitively, moving up the stack of MDPs captures the notion of identifying smaller, easier sub-goals within the problem.
+In terms of execution, a learning agent always begins at the base level MDP; whenever an action must be selected at a lower level, the current state information is fed upward and mapped to the next highest level of the AMDP effectively forcing the agent to think at one higher level of abstraction.
+This process repeats until the top of the MDP stack is reached, at which point, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level (which is then stored and reused so as to avoid redundant computation).
+Given this policy, the action required at highest level of abstraction becomes known and a series of surjective state mappings are maintained from higher to lower level MDPs allowing for a sort of backpropagation to occur once a higher level sub-task has been solved.
+This process of mapping backwards, computing a policy, and taking the specified action then repeats all the way down back to the base level MDP.
+It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs each of which is decreasing in size and complexity as we move up the AMDP stack.
 
-We show that grounding an arbitrary natural language command to a reward function will be most successful when the natural language command and MDP correspond to the same level of abstraction.
-For the purpose of staying consistent with the experimental method used by MacGlashan et.al., we will leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within BURLAP to conduct experiments and collect results.
+\section{Evaluation}
 
-\section{Section}
+\subsection{Experiments}
 
-Section text here.
+In order to examine the effectiveness of the abstractions imposed by these Abstract Markov Decision Processes (AMDPs), we extend prior work by MacGlashan et.
+al.
+on grounding natural language commands to the reward function of a Markov Decision Process (MDP).
+The primary contribution of this prior work is the ability to represent tasks as MDP reward functions and further combine learning from demonstration methods with language models to directly embed a user's verbal command into the reward function~\cite{MacGlashan2015GroundingEC}.
+Specifically, given a dataset of natural language commands and their associated task demonstrations, inverse reinforcement learning (IRL) is applied to the demonstrations in order to inform a distribution over possible reward functions which is then used to train a language model in a weakly supervised fashion.
+The authors followed the paradigm set up in MacGlashan et.
+al.
+and used an IBM Model II Translation System for translating between natural language and reward functions (machine language), augmented by the provided demonstration.
+More specifically, we modify the IBM Model II decoding procedure to weight the probability of a given translation (the probability of a machine language command given the source language command) by the probability of the machine language command given the provided demonstration.
+With this process, the success of the resultant models in grounding reward function tasks is dependent on both the various natural language commands across the dataset as well as the provided demonstrations.
 
-\subsection{Subsection Heading Here}
-Subsection text here.
+We show that grounding an arbitrary natural language command to a reward function will be most successful when the natural language command and reward function correspond to the same level of abstraction.
+Staying consistent with the experimental method used by MacGlashan et.al., we leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within the Brown-UMBC Reinforcement Learning and Planning library (BURLAP) to conduct our experiments.
+As with MacGlashan et.
+al.
+we use the Cleanup World Domain inspired by Sokoban \cite{Junghanns2001SokobanEG}.
+% INSERT FIGURE
 
-\subsubsection{Subsubsection Heading Here}
-Subsubsection text here.
+We build our own AMDP over this domain, with each level corresponding to a different level of abstraction.
+There are three levels: \textbf{low}, \textbf{mid}, and \textbf{high}.
+The low-level MDP corresponds to simple directional commands, like telling the agent to move north, south, east, and west.
+The mid-level MDP corresponds to commands referencing the agent, the block, the doors in each of the domain's three rooms, and the rooms themselves.
+Finally, the high-level MDP abstracts away doors, so that these commands only reference agents, blocks, and rooms.
 
-\section{RSS citations}
+To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands and their respective demonstrations.
+The following are some examples of natural language commands at each level of the AMDP:
 
-Please make sure to include \verb!natbib.sty! and to use the
-\verb!plainnat.bst! bibliography style. \verb!natbib! provides additional
-citation commands, most usefully \verb!\citet!. For example, rather than the
-awkward construction
+\begin{description}
+\item[\textbf{Low:}] Go three steps south, then two steps east.
+\item[\textbf{Mid:}] Go to the red door, then go into the red room.
+\item[\textbf{High:}] Go to the green room.
+\end{description}
 
-{\small
-\begin{verbatim}
-\cite{kalman1960new} demonstrated...
-\end{verbatim}
-}
+Our experiment consists of training IBM II Translation Models between every permutation of the levels of the AMDP.
+More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP.
+We then
+\subsection{Results}
 
-\noindent
-rendered as ``\cite{kalman1960new} demonstrated...,''
-or the
-inconvenient
-
-{\small
-\begin{verbatim}
-Kalman \cite{kalman1960new}
-demonstrated...
-\end{verbatim}
-}
-
-\noindent
-rendered as
-``Kalman \cite{kalman1960new} demonstrated...'',
-one can
-write
-
-{\small
-\begin{verbatim}
-\citet{kalman1960new} demonstrated...
-\end{verbatim}
-}
-\noindent
-which renders as ``\citet{kalman1960new} demonstrated...'' and is
-both easy to write and much easier to read.
-
-\subsection{RSS Hyperlinks}
-
-This year, we would like to use the ability of PDF viewers to interpret
-hyperlinks, specifically to allow each reference in the bibliography to be a
-link to an online version of the reference.
-As an example, if you were to cite ``Passive Dynamic Walking''
-\cite{McGeer01041990}, the entry in the bibtex would read:
-
-{\small
-\begin{verbatim}
-@article{McGeer01041990,
-  author = {McGeer, Tad},
-  title = {\href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic Walking}},
-  volume = {9},
-  number = {2},
-  pages = {62-82},
-  year = {1990},
-  doi = {10.1177/027836499000900206},
-  URL = {http://ijr.sagepub.com/content/9/2/62.abstract},
-  eprint = {http://ijr.sagepub.com/content/9/2/62.full.pdf+html},
-  journal = {The International Journal of Robotics Research}
-}
-\end{verbatim}
-}
-\noindent
-and the entry in the compiled PDF would look like:
-
-\def\tmplabel#1{[#1]}
-
-\begin{enumerate}
-\item[\tmplabel{1}] Tad McGeer. \href{http://ijr.sagepub.com/content/9/2/62.abstract}{Passive Dynamic
-Walking}. {\em The International Journal of Robotics Research}, 9(2):62--82,
-1990.
-\end{enumerate}
-%
-where the title of the article is a link that takes you to the article on IJRR's website.
-
-Linking cited articles will not always be possible, especially for
-older articles. There are also often several versions of papers
-online: authors are free to decide what to use as the link destination
-yet we strongly encourage to link to archival or publisher sites
-(such as IEEE Xplore or Sage Journals).  We encourage all authors to use this feature to
-the extent possible.
+Lorem ipsum
 
@@
 
-The conclusion goes here.
+Lorem ipsum
 

### 2016-05-05 paper/paper-template-latex/paper_template.tex
Add paper update

@@
 
-To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands and their respective demonstrations.
+To test the effectiveness of using AMDPs, we collect datasets for each level, with each dataset consisting of a list of natural language commands that match the given level's abstraction and their respective demonstrations.
 The following are some examples of natural language commands at each level of the AMDP:
@@
 More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP.
-We then
+We then evaluate the models by passing in a natural language command of a given level into each of the three models.
+In this ``swap'', we show that we get the best results for a given level of the AMDP with the corresponding natural language command, rather than any others.
+We use Leave-One-Out (LOO) accuracy as the evaluation metric.
+
 \subsection{Results}
 
-Lorem ipsum
+The following table shows our LOO results for each swap.
+The rows are labeled with the level of the Natural Language (NLP) command, while the Columns designate the level of the MDP to which the language is grounded (the level-specific IBM II Translation system.)
 
-\section{Conclusion}
+\begin{table}[h!]
+\centering
+\caption{LOO Accuracy for each Swap}
+\label{my-label}
+\begin{tabular}{l|l|l|l|}
+\cline{2-4}
+                                  & MDP Level 0 & MDP Level 1 & MDP Level 2 \\ \hline
+\multicolumn{1}{|l|}{NLP Level 0} & 0.0 \%      & 0.0\%       & 0.0\%       \\ \hline
+\multicolumn{1}{|l|}{NLP Level 1} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
+\multicolumn{1}{|l|}{NLP Level 2} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
+\end{tabular}
+\end{table}
+
+\section{Conclusion and Future Work}
 \label{sec:conclusion}
@@
 Lorem ipsum
-
-\section*{Acknowledgments}
 

### 2016-05-05 src/commands/amdp/domain/CleanupDomainDriver.java
Finished collecting L2L0 episode analysis

@@ -295,8 +295,8 @@ public class CleanupDomainDriver {
 	public static ValueFunctionInitialization getL0Heuristic(State s, RewardFunction rf){
 
 		double discount = 0.99;
-		// prop name if block -> block and room if 
-		CleanupL1AMDPDomain.GroundedPropSC rfCondition = (CleanupL1AMDPDomain.GroundedPropSC)((PullCostGoalRF)rf).getGoalCondition();
+		// prop name if block -> block and room if
+		CleanupL2AMDPDomain.GroundedPropSC rfCondition = (CleanupL2AMDPDomain.GroundedPropSC)((PullCostGoalRF)rf).getGoalCondition();
 		String PFName = rfCondition.gp.pf.getName();
 		String[] params = rfCondition.gp.params;
 		if(PFName.equals(CleanupWorld.PF_AGENT_IN_ROOM)){
@@ -312,7 +312,10 @@ public class CleanupDomainDriver {
 			return new BlockToRegionHeuristic(params[0], params[1], discount, lockProb);
 		}
 		else if(PFName.equals(CleanupWorld.PF_BLOCK_IN_DOOR + " " + CleanupWorld.PF_AGENT_IN_DOOR)){
-			return new JointHeuristic(new BlockToRegionHeuristic(params[0], params[1], discount, lockProb), new AgentToRegionHeuristic(params[1], discount, lockProb));
+			return new JointHeuristic(new BlockToRegionHeuristic(params[0], params[1], discount, lockProb), new AgentToRegionHeuristic(params[3], discount, lockProb));
+		}
+		else if(PFName.equals(CleanupWorld.PF_BLOCK_IN_ROOM + " " + CleanupWorld.PF_AGENT_IN_ROOM)){
+			return new JointHeuristic(new BlockToRegionHeuristic(params[0], params[1], discount, lockProb), new AgentToRegionHeuristic(params[3], discount, lockProb));
 		}
 		throw new RuntimeException("Unknown Reward Function with propositional function " + PFName + ". Cannot construct l0 heuristic.");
 	}

### 2016-05-05 src/commands/amdp/domain/CleanupL2AMDPDomain.java

@@ -281,6 +281,23 @@ public class CleanupL2AMDPDomain implements DomainGenerator {
 		return new GoalConditionTF(sc);
 	}
 
+	public static class GroundedPropSC implements StateConditionTest{
+
+		public GroundedProp gp;
+
+		public GroundedPropSC(GroundedProp gp) {
+			this.gp = gp;
+		}
+
+		@Override
+		public boolean satisfies(State s) {
+			//			if(gp.isTrue(s)){
+			//				System.out.println("goal!!");
+			//			}
+			return gp.isTrue(s);
+		}
+	}
+
 
 	public static class DoorLockedSC implements StateConditionTest{
 

### 2016-05-05 src/commands/amdp/tools/CleanupDriverTest.java

@@ -40,8 +40,8 @@ public class CleanupDriverTest {
 
         List<PropositionalFunction> pfs = new ArrayList<>();
 
-        pfs.add(domain.getPropFunction(CleanupWorld.PF_BLOCK_IN_DOOR));
-        pfs.add(domain.getPropFunction(CleanupWorld.PF_AGENT_IN_DOOR));
+        pfs.add(domain.getPropFunction(CleanupWorld.PF_BLOCK_IN_ROOM));
+        pfs.add(domain.getPropFunction(CleanupWorld.PF_AGENT_IN_ROOM));
 
         StringBuilder sb = new StringBuilder();
         pfs.stream().map(PropositionalFunction::getName).forEach(n -> sb.append(n).append(" "));
@@ -51,17 +51,18 @@ public class CleanupDriverTest {
         String[] parameterClasses = paramClasses.toArray(new String[paramClasses.size()]);
 
 
-//        GroundedProp groundedProp = new GroundedProp(new JointPF(name, domain, parameterClasses, pfs), new String[]{"block0", "door0", "agent0", "door1"});
+        GroundedProp groundedProp = new GroundedProp(new JointPF(name, domain, parameterClasses, pfs), new String[]{"block0", "room1", "agent0", "room0"});
 
 
-        GroundedProp groundedProp = new GroundedProp(domain.getPropFunction(CleanupWorld.PF_BLOCK_IN_DOOR),  new String[]{"block0", "door1"});
+//        GroundedProp groundedProp = new GroundedProp(domain.getPropFunction(CleanupWorld.PF_BLOCK_IN_ROOM),  new String[]{"block0", "room2"});
 
 
-        StateConditionTest sc = new CleanupL1AMDPDomain.GroundedPropSC(groundedProp);
+//        StateConditionTest sc = new CleanupL1AMDPDomain.GroundedPropSC(groundedProp);
+        StateConditionTest sc = new CleanupL2AMDPDomain.GroundedPropSC(groundedProp);
         RewardFunction heuristicRF = new PullCostGoalRF(sc, 1., 0.);
 
 
-        CleanupL1AMDPDomain.GroundedPropSC l0sc = new CleanupL1AMDPDomain.GroundedPropSC(groundedProp);
+        CleanupL2AMDPDomain.GroundedPropSC l0sc = new CleanupL2AMDPDomain.GroundedPropSC(groundedProp);
         GoalBasedRF l0rf = new GoalBasedRF(l0sc, 1., 0.);
[…]

### 2016-05-05 src/commands/amdp/tools/trajectory/EpisodeToTrajectory.java
Add L2L0

@@ -109,8 +109,8 @@ public class EpisodeToTrajectory {
     }
 
     public static void main(String[] args) {
-        String episodeDirectory = "/Users/sidd/Projects/commandsToTasks/data/amdpData/L1L0/ea";
-        String outputDirectory = "/Users/sidd/Projects/commandsToTasks/data/amdpData/L1L0" +
+        String episodeDirectory = "/Users/sidd/Projects/commandsToTasks/data/amdpData/L2L0/ea";
+        String outputDirectory = "/Users/sidd/Projects/commandsToTasks/data/amdpData/L2L0" +
                 "/trajectory";
 
         File dir = new File(episodeDirectory);

### 2016-05-05 src/commands/amdp/experiments/CleanupAMDPExperiment.java
Added full set of experiments

@@ -106,6 +106,20 @@ public class CleanupAMDPExperiment {
 
     public static void main(String[] args) {
 
+        /**
+         * Initial experimental results (10 samples per dataset -- 9 datasets total)
+         * In pairs, first argument refers to level and second argument refers to language
+         * L0 = 0.3
+         * L1 = 0.0
+         * L2 = 0.1
+         * L0-L1 =
+         * L0-L2 =
+         * L1-L0 =
+         * L1-L2 =
+         * L2-L0 =
+         * L2-L1 =
+         */
+
 //        boolean cacheIRLResults = true;
         boolean cacheIRLResults = false;
 
@@ -120,11 +134,17 @@ public class CleanupAMDPExperiment {
 //            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
         }
 
-//        LOOTest(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE);
-//        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE);
-        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
+//        LOOTest(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE); //L0
+//        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE); //L1
+//        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
 
-//        LOOTest(l1Controller, l1Controller.L0CROSSDATASET, L1_TRAJ_CACHE);
-//        LOOTest(l2Controller, l2Controller.L0CROSSDATASET, L2_TRAJ_CACHE);
+        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
+//        LOOTest(l0Controller, l0Controller.L2CROSSDATASET, L0_TRAJ_CACHE); //L0-L2
+
+//        LOOTest(l1Controller, l1Controller.L0CROSSDATASET, L1_TRAJ_CACHE); //L1-L0
+//        LOOTest(l1Controller, l1Controller.L2CROSSDATASET, L1_TRAJ_CACHE); //L1-L2
+
[…]

### 2016-05-05 src/commands/amdp/experiments/cleanupL2/CleanupL2ControllerConstructor.java

@@ -28,7 +28,7 @@ public class CleanupL2ControllerConstructor implements ControllerConstructor {
 
     public static final String L0CROSSDATASET = "data/amdpData/L0L2/trajectory";
 
-    public static final String L2CROSSDATASET = "data/amdpData/L1L2/trajectory";
+    public static final String L1CROSSDATASET = "data/amdpData/L1L2/trajectory";
 
     public DomainGenerator domainGenerator;
     public Domain domain;

### 2016-05-05 src/commands/amdp/experiments/CleanupAMDPExperiment.java
Fixed L1L2 trajectory errors and collected initial results

@@ -48,7 +48,7 @@ public class CleanupAMDPExperiment {
     }
 
     public static void LOOTest(ControllerConstructor constructor, String pathToDataset, String pathToIRLCache){
-        Map<String,String> rfLabels = constructor.getExpertDatasetRFLabels();
+        Map<String,String> rfLabels = ControllerConstructor.getExpertDatasetRFLabels();
 
         //get source training data
         List<TrainingElement> dataset = constructor.getTrainingDataset(pathToDataset);
@@ -112,12 +112,12 @@ public class CleanupAMDPExperiment {
          * L0 = 0.3
          * L1 = 0.0
          * L2 = 0.1
-         * L0-L1 =
-         * L0-L2 =
-         * L1-L0 =
-         * L1-L2 =
-         * L2-L0 =
-         * L2-L1 =
+         * L0-L1 = 0.0
+         * L0-L2 = 0.0
+         * L1-L0 = 0.0
+         * L1-L2 = 0.2
+         * L2-L0 = 0.0
+         * L2-L1 = 0.1
          */
 
 //        boolean cacheIRLResults = true;
@@ -138,13 +138,13 @@ public class CleanupAMDPExperiment {
 //        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE); //L1
 //        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
 
-        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
+//        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
 //        LOOTest(l0Controller, l0Controller.L2CROSSDATASET, L0_TRAJ_CACHE); //L0-L2
-
+//
 //        LOOTest(l1Controller, l1Controller.L0CROSSDATASET, L1_TRAJ_CACHE); //L1-L0
 //        LOOTest(l1Controller, l1Controller.L2CROSSDATASET, L1_TRAJ_CACHE); //L1-L2
 
 //        LOOTest(l2Controller, l2Controller.L0CROSSDATASET, L2_TRAJ_CACHE); //L2-L0
-//        LOOTest(l2Controller, l2Controller.L1CROSSDATASET, L2_TRAJ_CACHE); //L2-L1
[…]

### 2016-05-05 src/commands/amdp/experiments/ControllerConstructor.java

@@ -5,6 +5,7 @@ import burlap.oomdp.legacy.StateParser;
 import commands.data.TrainingElement;
 import commands.model3.weaklysupervisedinterface.WeaklySupervisedController;
 
+import java.util.HashMap;
 import java.util.List;
 import java.util.Map;
 
@@ -19,13 +20,59 @@ public interface ControllerConstructor {
 
     public List<TrainingElement> getTrainingDataset(String pathToDatasetDir);
 
-    public Map<String, String> getExpertDatasetRFLabels();
+    public static Map<String, String> getExpertDatasetRFLabels(){
+        Map<String, String> labels = new HashMap<>();
+
+        //L0
+        labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
+        labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|one|step|north|one|step|west.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|one|step|north|two|steps|south.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|one|step|south|one|step|east.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|one|step|west.txt", "agentInRoom(agent0, room2)");
+        labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
+        labels.put("move|three|steps|south|one|step|north.txt", "agentInRoom(agent0, room0)");
+        labels.put("move|three|steps|south|one|step|west.txt", "agentInRoom(agent0, room0)");
+
+        //L1
+        labels.put("go|to|red|door|go|into|red|room.txt", "agentInRegion(agent0, room0)");
+        labels.put("go|to|red|door|go|into|red|room|go|to|green|door.txt", "agentInRegion(agent0, door1)");
+        labels.put("go|to|red|door|go|into|red|room|go|to|green|door|go|into|green|room.txt", "agentInRegion(agent0, room1)");
+        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|go|to|red|door.txt", "agentInRegion(agent0, door0)");
+        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|move|to|green|door|move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
[…]

### 2016-05-05 src/commands/amdp/experiments/cleanupL0/CleanupL0ControllerConstructor.java

@@ -84,24 +84,24 @@ public class CleanupL0ControllerConstructor implements ControllerConstructor {
         return dataset;
     }
 
-    @Override
-    public Map<String, String> getExpertDatasetRFLabels() {
-
-        Map<String, String> labels = new HashMap<>();
-
-        labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
-        labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north|one|step|west.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north|two|steps|south.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|south|one|step|east.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|west.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
-        labels.put("move|three|steps|south|one|step|north.txt", "agentInRoom(agent0, room0)");
-        labels.put("move|three|steps|south|one|step|west.txt", "agentInRoom(agent0, room0)");
-
-        return labels;
-    }
+//    @Override
+//    public Map<String, String> getExpertDatasetRFLabels() {
+//
+//        Map<String, String> labels = new HashMap<>();
+//
+//        labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
+//        labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|one|step|north|one|step|west.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|one|step|north|two|steps|south.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|one|step|south|one|step|east.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|one|step|west.txt", "agentInRoom(agent0, room2)");
+//        labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
[…]

### 2016-05-05 src/commands/amdp/experiments/cleanupL1/CleanupL1ControllerConstructor.java

@@ -100,23 +100,22 @@ public class CleanupL1ControllerConstructor implements ControllerConstructor{
         return this.cacheStateParser;
     }
 
-    //This is how we get the right "answer" - the RF produced by the model is compared to the string here
-    @Override
-    public Map<String, String> getExpertDatasetRFLabels(){
-
-        Map<String, String> labels = new HashMap<>();
-
-        labels.put("go|to|red|door|go|into|red|room.txt", "agentInRegion(agent0, room0)");
-        labels.put("go|to|red|door|go|into|red|room|go|to|green|door.txt", "agentInRegion(agent0, door1)");
-        labels.put("go|to|red|door|go|into|red|room|go|to|green|door|go|into|green|room.txt", "agentInRegion(agent0, room1)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|go|to|red|door.txt", "agentInRegion(agent0, door0)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|move|to|green|door|move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door.txt", "blockInRegion(block0, door0)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|go|to|green|door.txt", "agentInRegion(agent0, door0) blockInRegion(block0, door0)");
-        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|move|to|red|door|move|bag|to|red|room.txt", "blockInRegion(block0, room0)");
-        labels.put("go|to|red|door|go|to|blue|room.txt", "agentInRegion(agent0, room2)");
-        labels.put("go|to|red|door|go|to|red|room|move|bag|to|green|door.txt", "blockInRegion(block0, door1)");
-
-        return labels;
-    }
+//    @Override
+//    public Map<String, String> getExpertDatasetRFLabels(){
+//
+//        Map<String, String> labels = new HashMap<>();
+//
+//        labels.put("go|to|red|door|go|into|red|room.txt", "agentInRegion(agent0, room0)");
+//        labels.put("go|to|red|door|go|into|red|room|go|to|green|door.txt", "agentInRegion(agent0, door1)");
[…]

### 2016-05-05 src/commands/amdp/experiments/cleanupL2/CleanupL2ControllerConstructor.java

@@ -89,26 +89,26 @@ public class CleanupL2ControllerConstructor implements ControllerConstructor {
         return this.cacheStateParser;
     }
 
-    @Override
-    public Map<String, String> getExpertDatasetRFLabels() {
-        Map<String, String> labels = new HashMap<>();
-
-        labels.put("go|to|the|green|room.txt", "agentInRegion(agent0, room1)");
-        labels.put("go|to|the|red|room.txt", "agentInRegion(agent0, room0)");
-        labels.put("move|bag|to|blue|room.txt", "blockInRegion(block0, room2)");
-        labels.put("move|bag|to|blue|room|and|then|go|to|the|green|room.txt", "agentInRegion" +
-                        "(agent0, room1) blockInRegion(block0, room2)");
-        labels.put("move|bag|to|blue|room|and|then|go|to|the|red|room.txt", "agentInRegion" +
-                        "(agent0, room0) blockInRegion(block0, room2)");
-        labels.put("move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
-        labels.put("move|bag|to|green|room|and|then|go|to|the|blue|room.txt", "agentInRegion" +
-                "(agent0, room2) blockInRegion(block0, room1)");
-        labels.put("move|bag|to|green|room|then|move|bag|to|blue|room.txt", "blockInRegion" +
-                "(block0, room2)");
-        labels.put("move|bag|to|the|green|room|then|go|to|the|green|room.txt", "agentInRegion" +
-                "(agent0, room1) blockInRegion(block0, room1)");
-        labels.put("move|bag|to|the|green|room|then|go|to|the|red|room.txt", "agentInRegion" +
-                "(agent0, room0) blockInRegion(block0, room1)");
-        return labels;
-    }
+//    @Override
+//    public Map<String, String> getExpertDatasetRFLabels() {
+//        Map<String, String> labels = new HashMap<>();
+//
+//        labels.put("go|to|the|green|room.txt", "agentInRegion(agent0, room1)");
+//        labels.put("go|to|the|red|room.txt", "agentInRegion(agent0, room0)");
+//        labels.put("move|bag|to|blue|room.txt", "blockInRegion(block0, room2)");
+//        labels.put("move|bag|to|blue|room|and|then|go|to|the|green|room.txt", "agentInRegion" +
+//                        "(agent0, room1) blockInRegion(block0, room2)");
[…]

### 2016-05-09 src/commands/amdp/experiments/CleanupAMDPExperiment.java
Added authors to paper and resolved RF labels

@@ -81,6 +81,10 @@ public class CleanupAMDPExperiment {
             GenerativeModel gm = controller.getGM();
             TrainingElement queryElement = dataset.get(i);
             String rfLabel = rfLabels.get(queryElement.identifier);
+            if(rfLabel == null){
+                System.out.println(queryElement.identifier);
+                throw new RuntimeException("Encountered element of dataset without corresponding true RF label!");
+            }
             List<GMQueryResult> rfDist = controller.getRFDistribution(queryElement.trajectory.getState(0), queryElement.command);
             GMQueryResult predicted = GMQueryResult.maxProb(rfDist);
 
@@ -131,12 +135,12 @@ public class CleanupAMDPExperiment {
         if(cacheIRLResults) {
 //            cacheIRLResultsFor(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE);
 //            cacheIRLResultsFor(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE);
-//            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
+            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
         }
 
 //        LOOTest(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE); //L0
 //        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE); //L1
-//        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
+        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
 
 //        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
 //        LOOTest(l0Controller, l0Controller.L2CROSSDATASET, L0_TRAJ_CACHE); //L0-L2
@@ -145,6 +149,6 @@ public class CleanupAMDPExperiment {
 //        LOOTest(l1Controller, l1Controller.L2CROSSDATASET, L1_TRAJ_CACHE); //L1-L2
 
 //        LOOTest(l2Controller, l2Controller.L0CROSSDATASET, L2_TRAJ_CACHE); //L2-L0
[…]

### 2016-05-09 src/commands/amdp/experiments/ControllerConstructor.java

@@ -24,6 +24,17 @@ public interface ControllerConstructor {
         Map<String, String> labels = new HashMap<>();
 
         //L0
+        labels.put("go|east|for|one|step|then|south|for|one|step|then|north|for|two|steps.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step|then|go|south|for|two|steps.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step|then|west|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|south|for|four|steps|then|west|for|four|steps.txt", "agentInRoom(agent0, room0)");
+        labels.put("go|south|for|one|step|then|east|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|south|for|three|steps|then|go|east|for|one|step.txt", "agentInRoom(agent0, room0)");
+        labels.put("go|south|for|three|steps|then|go|north|for|one|step.txt", "agentInRoom(agent0, room0)");
+        labels.put("go|south|for|three|steps|then|go|west|for|one|step.txt", "agentInRoom(agent0, room0)");
+        labels.put("go|west|for|one|step.txt", "agentInRoom(agent0, room2)");
+
         labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
         labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
         labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
@@ -34,6 +45,17 @@ public interface ControllerConstructor {
         labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
         labels.put("move|three|steps|south|one|step|north.txt", "agentInRoom(agent0, room0)");
         labels.put("move|three|steps|south|one|step|west.txt", "agentInRoom(agent0, room0)");
+
+        labels.put("walk|east|one|step|then|go|south|one|step|then|go|north|two|steps.txt", "agentInRoom(agent0, room2)");
+        labels.put("walk|north|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("walk|north|one|step|then|go|south|one|step.txt", "agentInRoom(agent0, room2)");
[…]

### 2016-05-09 src/commands/amdp/experiments/CleanupAMDPExperiment.java
Restructured controller constructors -- will rerun experiments

@@ -48,7 +48,7 @@ public class CleanupAMDPExperiment {
     }
 
     public static void LOOTest(ControllerConstructor constructor, String pathToDataset, String pathToIRLCache){
-        Map<String,String> rfLabels = ControllerConstructor.getExpertDatasetRFLabels();
+        Map<String,String> rfLabels = constructor.getExpertDatasetRFLabels();
 
         //get source training data
         List<TrainingElement> dataset = constructor.getTrainingDataset(pathToDataset);
@@ -124,6 +124,20 @@ public class CleanupAMDPExperiment {
          * L2-L1 = 0.1
          */
 
+        /**
+         * Initial experimental results (30 samples per dataset -- 9 datasets total)
+         * In pairs, first argument refers to level and second argument refers to language
+         * L0 = 0.367
+         * L1 = 0.0357 (only 28 samples?)
+         * L2 = 0.1
+         * L0-L1 =
+         * L0-L2 =
+         * L1-L0 =
+         * L1-L2 = 0.2
+         * L2-L0 =
+         * L2-L1 = 0.107 (only 28 samples?)
+         */
+
 //        boolean cacheIRLResults = true;
         boolean cacheIRLResults = false;
 
@@ -135,15 +149,15 @@ public class CleanupAMDPExperiment {
         if(cacheIRLResults) {
 //            cacheIRLResultsFor(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE);
 //            cacheIRLResultsFor(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE);
-            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
+//            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
         }
 
 //        LOOTest(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE); //L0
 //        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE); //L1
-        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
[…]

### 2016-05-09 src/commands/amdp/experiments/ControllerConstructor.java

@@ -20,143 +20,145 @@ public interface ControllerConstructor {
 
     public List<TrainingElement> getTrainingDataset(String pathToDatasetDir);
 
-    public static Map<String, String> getExpertDatasetRFLabels(){
-        Map<String, String> labels = new HashMap<>();
+    public Map<String, String> getExpertDatasetRFLabels();
 
-        //L0
-        labels.put("go|east|for|one|step|then|south|for|one|step|then|north|for|two|steps.txt", "agentInRoom(agent0, room2)");
-        labels.put("go|north|for|one|step.txt", "agentInRoom(agent0, room2)");
-        labels.put("go|north|for|one|step|then|go|south|for|two|steps.txt", "agentInRoom(agent0, room2)");
-        labels.put("go|north|for|one|step|then|west|for|one|step.txt", "agentInRoom(agent0, room2)");
-        labels.put("go|south|for|four|steps|then|west|for|four|steps.txt", "agentInRoom(agent0, room0)");
-        labels.put("go|south|for|one|step|then|east|for|one|step.txt", "agentInRoom(agent0, room2)");
-        labels.put("go|south|for|three|steps|then|go|east|for|one|step.txt", "agentInRoom(agent0, room0)");
-        labels.put("go|south|for|three|steps|then|go|north|for|one|step.txt", "agentInRoom(agent0, room0)");
-        labels.put("go|south|for|three|steps|then|go|west|for|one|step.txt", "agentInRoom(agent0, room0)");
-        labels.put("go|west|for|one|step.txt", "agentInRoom(agent0, room2)");
-
-        labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
-        labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north|one|step|west.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|north|two|steps|south.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|south|one|step|east.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|one|step|west.txt", "agentInRoom(agent0, room2)");
-        labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
[…]

### 2016-05-09 src/commands/amdp/experiments/cleanupL0/CleanupL0ControllerConstructor.java

@@ -84,24 +84,144 @@ public class CleanupL0ControllerConstructor implements ControllerConstructor {
         return dataset;
     }
 
-//    @Override
-//    public Map<String, String> getExpertDatasetRFLabels() {
-//
-//        Map<String, String> labels = new HashMap<>();
-//
-//        labels.put("move|four|steps|south|four|steps|west.txt", "agentInRoom(agent0, room0)");
-//        labels.put("move|one|step|east|one|step|south|then|two|steps|north.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|one|step|north.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|one|step|north|one|step|west.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|one|step|north|two|steps|south.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|one|step|south|one|step|east.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|one|step|west.txt", "agentInRoom(agent0, room2)");
-//        labels.put("move|three|steps|south|one|step|east.txt", "agentInRoom(agent0, room0)");
-//        labels.put("move|three|steps|south|one|step|north.txt", "agentInRoom(agent0, room0)");
-//        labels.put("move|three|steps|south|one|step|west.txt", "agentInRoom(agent0, room0)");
-//
-//        return labels;
-//    }
+    @Override
+    public Map<String, String> getExpertDatasetRFLabels() {
+        Map<String, String> labels = new HashMap<>();
+
+        //L0
+        labels.put("go|east|for|one|step|then|south|for|one|step|then|north|for|two|steps.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step|then|go|south|for|two|steps.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|north|for|one|step|then|west|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|south|for|four|steps|then|west|for|four|steps.txt", "agentInRoom(agent0, room0)");
+        labels.put("go|south|for|one|step|then|east|for|one|step.txt", "agentInRoom(agent0, room2)");
+        labels.put("go|south|for|three|steps|then|go|east|for|one|step.txt", "agentInRoom(agent0, room0)");
[…]

### 2016-05-09 src/commands/amdp/experiments/cleanupL1/CleanupL1ControllerConstructor.java

@@ -100,22 +100,142 @@ public class CleanupL1ControllerConstructor implements ControllerConstructor{
         return this.cacheStateParser;
     }
 
-//    @Override
-//    public Map<String, String> getExpertDatasetRFLabels(){
-//
-//        Map<String, String> labels = new HashMap<>();
-//
-//        labels.put("go|to|red|door|go|into|red|room.txt", "agentInRegion(agent0, room0)");
-//        labels.put("go|to|red|door|go|into|red|room|go|to|green|door.txt", "agentInRegion(agent0, door1)");
-//        labels.put("go|to|red|door|go|into|red|room|go|to|green|door|go|into|green|room.txt", "agentInRegion(agent0, room1)");
-//        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|go|to|red|door.txt", "agentInRegion(agent0, door0)");
-//        labels.put("go|to|red|door|go|into|red|room|move|bag|to|green|door|move|to|green|door|move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
-//        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door.txt", "blockInRegion(block0, door0)");
-//        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|go|to|green|door.txt", "agentInRegion(agent0, door0) blockInRegion(block0, door0)");
-//        labels.put("go|to|red|door|go|into|red|room|move|bag|to|red|door|move|to|red|door|move|bag|to|red|room.txt", "blockInRegion(block0, room0)");
-//        labels.put("go|to|red|door|go|to|blue|room.txt", "agentInRegion(agent0, room2)");
-//        labels.put("go|to|red|door|go|to|red|room|move|bag|to|green|door.txt", "blockInRegion(block0, door1)");
-//
-//        return labels;
-//    }
+    @Override
+    public Map<String, String> getExpertDatasetRFLabels(){
+        Map<String, String> labels = new HashMap<>();
+
+        //L0
+        labels.put("go|east|for|one|step|then|south|for|one|step|then|north|for|two|steps.txt", "agentInRegion(agent0, room2)");
+        labels.put("go|north|for|one|step.txt", "agentInRegion(agent0, room2)");
+        labels.put("go|north|for|one|step|then|go|south|for|two|steps.txt", "agentInRegion(agent0, room2)");
+        labels.put("go|north|for|one|step|then|west|for|one|step.txt", "agentInRegion(agent0, room2)");
[…]

### 2016-05-09 src/commands/amdp/experiments/cleanupL2/CleanupL2ControllerConstructor.java

@@ -89,26 +89,142 @@ public class CleanupL2ControllerConstructor implements ControllerConstructor {
         return this.cacheStateParser;
     }
 
-//    @Override
-//    public Map<String, String> getExpertDatasetRFLabels() {
-//        Map<String, String> labels = new HashMap<>();
-//
-//        labels.put("go|to|the|green|room.txt", "agentInRegion(agent0, room1)");
-//        labels.put("go|to|the|red|room.txt", "agentInRegion(agent0, room0)");
-//        labels.put("move|bag|to|blue|room.txt", "blockInRegion(block0, room2)");
-//        labels.put("move|bag|to|blue|room|and|then|go|to|the|green|room.txt", "agentInRegion" +
-//                        "(agent0, room1) blockInRegion(block0, room2)");
-//        labels.put("move|bag|to|blue|room|and|then|go|to|the|red|room.txt", "agentInRegion" +
-//                        "(agent0, room0) blockInRegion(block0, room2)");
-//        labels.put("move|bag|to|green|room.txt", "blockInRegion(block0, room1)");
-//        labels.put("move|bag|to|green|room|and|then|go|to|the|blue|room.txt", "agentInRegion" +
-//                "(agent0, room2) blockInRegion(block0, room1)");
-//        labels.put("move|bag|to|green|room|then|move|bag|to|blue|room.txt", "blockInRegion" +
-//                "(block0, room2)");
-//        labels.put("move|bag|to|the|green|room|then|go|to|the|green|room.txt", "agentInRegion" +
-//                "(agent0, room1) blockInRegion(block0, room1)");
-//        labels.put("move|bag|to|the|green|room|then|go|to|the|red|room.txt", "agentInRegion" +
-//                "(agent0, room0) blockInRegion(block0, room1)");
-//        return labels;
-//    }
+    @Override
+    public Map<String, String> getExpertDatasetRFLabels() {
+        Map<String, String> labels = new HashMap<>();
+
+        //L0
+        labels.put("go|east|for|one|step|then|south|for|one|step|then|north|for|two|steps.txt", "agentInRegion(agent0, room2)");
+        labels.put("go|north|for|one|step.txt", "agentInRegion(agent0, room2)");
+        labels.put("go|north|for|one|step|then|go|south|for|two|steps.txt", "agentInRegion(agent0, room2)");
[…]

### 2016-05-09 src/commands/amdp/experiments/CleanupAMDPExperiment.java
Fixed RF label errors and added new experimental results

@@ -113,6 +113,7 @@ public class CleanupAMDPExperiment {
         /**
          * Initial experimental results (10 samples per dataset -- 9 datasets total)
          * In pairs, first argument refers to level and second argument refers to language
+         * NOTE: These results may be invalid since the RF label mappings were incorrect
          * L0 = 0.3
          * L1 = 0.0
          * L2 = 0.1
@@ -130,12 +131,12 @@ public class CleanupAMDPExperiment {
          * L0 = 0.367
          * L1 = 0.0357 (only 28 samples?)
          * L2 = 0.1
-         * L0-L1 =
-         * L0-L2 =
-         * L1-L0 =
-         * L1-L2 = 0.2
-         * L2-L0 =
-         * L2-L1 = 0.107 (only 28 samples?)
+         * L0-L1 = 0.107 (only 28 samples?)
+         * L0-L2 = 0.467
+         * L1-L0 = 0.0
+         * L1-L2 = 0.267
+         * L2-L0 = 0.4
+         * L2-L1 = 0.143 (only 28 samples?)
          */
 
 //        boolean cacheIRLResults = true;
@@ -156,8 +157,8 @@ public class CleanupAMDPExperiment {
 //        LOOTest(l1Controller, l1Controller.EXPERTDATASET, L1_TRAJ_CACHE); //L1
 //        LOOTest(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE); //L2
 
-//        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
-        LOOTest(l0Controller, l0Controller.L2CROSSDATASET, L0_TRAJ_CACHE); //L0-L2
+        LOOTest(l0Controller, l0Controller.L1CROSSDATASET, L0_TRAJ_CACHE); //L0-L1
+//        LOOTest(l0Controller, l0Controller.L2CROSSDATASET, L0_TRAJ_CACHE); //L0-L2
 //
 //        LOOTest(l1Controller, l1Controller.L0CROSSDATASET, L1_TRAJ_CACHE); //L1-L0
 //        LOOTest(l1Controller, l1Controller.L2CROSSDATASET, L1_TRAJ_CACHE); //L1-L2

### 2016-05-09 src/commands/amdp/experiments/cleanupL0/CleanupL0ControllerConstructor.java

@@ -203,12 +203,12 @@ public class CleanupL0ControllerConstructor implements ControllerConstructor {
 
         labels.put("move|to|green|room.txt", "agentInRoom(agent0, room1)");
         labels.put("move|to|red|room.txt", "agentInRoom(agent0, room0)");
-        labels.put("take|bag|to|blue|room.txt", "blockInRoom(agent0, room2)");
+        labels.put("take|bag|to|blue|room.txt", "blockInRoom(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|green|room.txt",
                 "agentInRoom(agent0, room1) blockInRoom(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|red|room.txt",
                 "agentInRoom(agent0, room0) blockInRoom(block0, room2)");
-        labels.put("take|bag|to|green|room.txt", "blockInRoom(agent0, room1)");
+        labels.put("take|bag|to|green|room.txt", "blockInRoom(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|blue|room.txt",
                 "agentInRoom(agent0, room2) blockInRoom(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|green|room.txt",

### 2016-05-09 src/commands/amdp/experiments/cleanupL1/CleanupL1ControllerConstructor.java

@@ -219,12 +219,12 @@ public class CleanupL1ControllerConstructor implements ControllerConstructor{
 
         labels.put("move|to|green|room.txt", "agentInRegion(agent0, room1)");
         labels.put("move|to|red|room.txt", "agentInRegion(agent0, room0)");
-        labels.put("take|bag|to|blue|room.txt", "blockInRegion(agent0, room2)");
+        labels.put("take|bag|to|blue|room.txt", "blockInRegion(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|green|room.txt",
                 "agentInRegion(agent0, room1) blockInRegion(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|red|room.txt",
                 "agentInRegion(agent0, room0) blockInRegion(block0, room2)");
-        labels.put("take|bag|to|green|room.txt", "blockInRegion(agent0, room1)");
+        labels.put("take|bag|to|green|room.txt", "blockInRegion(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|blue|room.txt",
                 "agentInRegion(agent0, room2) blockInRegion(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|green|room.txt",

### 2016-05-09 src/commands/amdp/experiments/cleanupL2/CleanupL2ControllerConstructor.java

@@ -208,12 +208,12 @@ public class CleanupL2ControllerConstructor implements ControllerConstructor {
 
         labels.put("move|to|green|room.txt", "agentInRegion(agent0, room1)");
         labels.put("move|to|red|room.txt", "agentInRegion(agent0, room0)");
-        labels.put("take|bag|to|blue|room.txt", "blockInRegion(agent0, room2)");
+        labels.put("take|bag|to|blue|room.txt", "blockInRegion(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|green|room.txt",
                 "agentInRegion(agent0, room1) blockInRegion(block0, room2)");
         labels.put("take|bag|to|blue|room|then|move|to|red|room.txt",
                 "agentInRegion(agent0, room0) blockInRegion(block0, room2)");
-        labels.put("take|bag|to|green|room.txt", "blockInRegion(agent0, room1)");
+        labels.put("take|bag|to|green|room.txt", "blockInRegion(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|blue|room.txt",
                 "agentInRegion(agent0, room2) blockInRegion(block0, room1)");
         labels.put("take|bag|to|green|room|then|move|to|green|room.txt",

### 2016-05-10 paper/paper-template-latex/paper_template.tex
Add results to paper
Added authors to paper and resolved RF labels
Finished draft of paper

@@
 \usepackage{times}
-
+\usepackage{graphicx}
 % numbers option provides compact numerical references in the text.
@@
 % You will get a Paper-ID when submitting a pdf file to the conference system
-\author{Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]}
+\author{%Author Names Omitted for Anonymous Review. Paper-ID [add your ID here]
+\authorblockN{Dilip Arumugam}
+\and
+\authorblockN{Sidd Karamcheti}
+\and
+\authorblockN{James MacGlashan}
+\and
+\authorblockN{Nakul Gopalan}
+\and
+\authorblockN{Stefanie Tellex}
+}
 
@@
 \begin{abstract}
-The abstract goes here.
+Deriving new methods of task decomposition has been central to the field of reinforcement learning.
+We examine a newly proposed method for hierarchical task decomposition known as abstract Markov decision processes (AMDPs) which maintains internal MDPs as natural layers of abstraction over some ``base'' input problem allowing for efficient planning.
+Inspired by prior work for grounding natural language to the reward function of a regular MDP, we consider the effect of grounding natural language with varying degrees of abstraction to the individual layers of abstraction within the AMDP.
+Hypothesizing that the accuracy of the grounding procedure would be greatest when the degree of abstraction between language and internal MDP match, we evaluate on all pairwise combinations.
+Our results, while proving our hypothesis to be incorrect, suggest that the AMDP framework has great potential for task decomposition as it captures logical relationships between layers of abstraction within the AMDP.
 \end{abstract}
@@
 Developing good methods of abstraction represents a logical way to accelerate planning time by breaking apart large, complex tasks into smaller sub-tasks.
-Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and achieving sub-goals.
-Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilize multiple layers of abstraction over all components of the Markov Decision Process (MPD) in order to efficiently learn in complex domains.
-In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the abstraction based on the success of these groundings.
+Moreover, this notion of decomposing tasks into their smaller constituent pieces more closely resembles our own human methodology for solving problems by identifying and completing sub-goals.
+Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilizes multiple layers of abstraction over all components of the Markov Decision Process (MDP) in order to efficiently learn in complex domains.
+In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the succeess of the grounding process as a measure of the strength of the abstraction.
 
 \section{Prior Work}
-Typically, methods of abstraction have been applied to only a single element of the standard Markov decision process (MDP) formalism in the hopes of improving overall problem tractability.
+Typically, methods of abstraction have been applied to only a single element of an MDP in the hopes of improving overall problem tractability.
 Specifically, there have been some approaches that attempt to perform state abstraction~\cite{Li2006TowardsAU} by compressing similar states into single units or intelligently pruning states that are irrelevant to the overall task from consideration.
-Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``action''.
+Other approaches examine abstraction over the action space via macro-actions~\cite{Hauskrecht1998HierarchicalSO} or options~\cite{Sutton1999BetweenMA} that compose sequences of atomic actions into a single ``larger'' or temporally extended action.
 Unfortunately, these methods suffer from potentially increasing the size of the state or action space thereby increasing the time needed for planning~\cite{Jong2008TheUO}.
@@
 
-Building on top of this, AMDPs take a layered approach by maintaining a stack of MDPs, each of which represents a different layer of abstraction for the input problem.
-The base (lowest) level MDP is always the MDP representing the original problem while higher level MDPs are hard coded over smaller state and action spaces (with corresponding transition dynamics and reward functions).
+Building on top of this, AMDPs take a layered approach by maintaining an internal stack of MDPs, each of which represents a different layer of abstraction over the input problem.
+The base (lowest) level MDP is always the MDP representing the original problem (i.e.
+the input MDP) while higher level MDPs are hard coded over smaller state and action spaces (with corresponding and distinct transition dynamics and reward functions).
 Each state and action in a higher level MDP is implemented as an abstraction over multiple states and actions in the lower level creating a many-to-one mapping (as we move up the stack) resulting in smaller, more tractable state-action spaces.
 Intuitively, moving up the stack of MDPs captures the notion of identifying smaller, easier sub-goals within the problem.
+
 In terms of execution, a learning agent always begins at the base level MDP; whenever an action must be selected at a lower level, the current state information is fed upward and mapped to the next highest level of the AMDP effectively forcing the agent to think at one higher level of abstraction.
 This process repeats until the top of the MDP stack is reached, at which point, standard reinforcement learning algorithms are applied in order to compute a stationary policy for the entire level (which is then stored and reused so as to avoid redundant computation).
-Given this policy, the action required at highest level of abstraction becomes known and a series of surjective state mappings are maintained from higher to lower level MDPs allowing for a sort of backpropagation to occur once a higher level sub-task has been solved.
-This process of mapping backwards, computing a policy, and taking the specified action then repeats all the way down back to the base level MDP.
+Given this policy, the action required at highest level of abstraction becomes known and is representative of a single sub-goal that need be solved in order to complete the overall task.
+A series of surjective state mappings are maintained from higher to lower level MDPs allowing for a sort of backpropagation to occur once the higher level sub-task has been identified.
+This process of mapping backwards, computing a policy, and taking the specified action then repeats all the way down back to the base level MDP at which the original high-level sub-goal is fully expanded into the set of lower level actions that represent the completion of the subgoal.
 It is important to note that since policies computed at each level of the AMDP are stored, the true cost of planning in an AMDP is only equivalent to the cost of planning and solving all higher level MDPs each of which is decreasing in size and complexity as we move up the AMDP stack.
@@
 
+\begin{figure}[tbp]
+\begin{center}
+\includegraphics[scale=0.12]{images/cleanup}
+\caption{\small An example of the CleanupWorld base level domain.
+}
+\end{center}
+\end{figure}
+
 \subsection{Experiments}
 
-In order to examine the effectiveness of the abstractions imposed by these Abstract Markov Decision Processes (AMDPs), we extend prior work by MacGlashan et.
-al.
-on grounding natural language commands to the reward function of a Markov Decision Process (MDP).
-The primary contribution of this prior work is the ability to represent tasks as MDP reward functions and further combine learning from demonstration methods with language models to directly embed a user's verbal command into the reward function~\cite{MacGlashan2015GroundingEC}.
+In order to examine the effectiveness of the abstractions imposed by the AMDP, we extend prior work on grounding natural language commands to the reward function of a Markov Decision Process (MDP).
+The primary contribution of this work is the ability to represent MDP reward functions as constrained conjunctions of propositional logic functions as well as combine learning from demonstration methods with language models to directly embed a user's verbal command into reward functions of the aforementioned form~\cite{MacGlashan2015GroundingEC}.
 Specifically, given a dataset of natural language commands and their associated task demonstrations, inverse reinforcement learning (IRL) is applied to the demonstrations in order to inform a distribution over possible reward functions which is then used to train a language model in a weakly supervised fashion.
-The authors followed the paradigm set up in MacGlashan et.
-al.
-and used an IBM Model II Translation System for translating between natural language and reward functions (machine language), augmented by the provided demonstration.
+Following directly from the work of MacGlashan et.
+al., we use an IBM Model II Translation System for translating between natural language and reward functions (machine language), augmented by the probability of the provided demonstration under IRL.
 More specifically, we modify the IBM Model II decoding procedure to weight the probability of a given translation (the probability of a machine language command given the source language command) by the probability of the machine language command given the provided demonstration.
-With this process, the success of the resultant models in grounding reward function tasks is dependent on both the various natural language commands across the dataset as well as the provided demonstrations.
+With this process, the success of the resultant models in grounding reward function tasks is dependent on both the variety of natural language commands across the dataset as well as the strength of the IRL procedure over the provided demonstrations.
+
+\subsection{Domain}
 
@@
 Staying consistent with the experimental method used by MacGlashan et.al., we leverage objected-oriented MDPs~\cite{Diuk2008AnOR} within the Brown-UMBC Reinforcement Learning and Planning library (BURLAP) to conduct our experiments.
-As with MacGlashan et.
-al.
-we use the Cleanup World Domain inspired by Sokoban \cite{Junghanns2001SokobanEG}.
+For similar reasons, we also use the CleanupWorld domain inspired by Sokoban \cite{Junghanns2001SokobanEG}.
+In Figure 1, we provide an image of the standard CleanupWorld domain in a standard start configuration.
 % INSERT FIGURE
 
-We build our own AMDP over this domain, with each level corresponding to a different level of abstraction.
-There are three levels: \textbf{low}, \textbf{mid}, and \textbf{high}.
-The low-level MDP corresponds to simple directional commands, like telling the agent to move north, south, east, and west.
-The mid-level MDP corresponds to commands referencing the agent, the block, the doors in each of the domain's three rooms, and the rooms themselves.
-Finally, the high-level MDP abstracts away doors, so that these commands only reference agents, blocks, and rooms.
+We build our own AMDP over this domain with three \textbf{low}, \textbf{mid}, and \textbf{high} levels such that each level corresponds to a different level of task abstraction.
+The low-level MDP corresponds to simple directional commands, where the action space consists of moving one step in the north, south, east, or west direction.
+The mid-level MDP abstracts over the low-level MDP and encapsulates sub-goals which move the agent and blocks to specific doors and, subsequently, rooms.
+Finally, the high-level MDP abstracts away the notion of doors and contains the sub-goals of moving an agent or block to a particular room.
 
@@
 
-Our experiment consists of training IBM II Translation Models between every permutation of the levels of the AMDP.
-More precisely, we train a model to translate a natural language command to a machine language reward function for each level of the AMDP.
+Our experiment consists of training demonstration weighted IBM II Translation Models between every permutation of the levels of the AMDP.
 We then evaluate the models by passing in a natural language command of a given level into each of the three models.
-In this ``swap'', we show that we get the best results for a given level of the AMDP with the corresponding natural language command, rather than any others.
+With this process, we hypothesized that the best results for a given level of the AMDP will match to natural language commands with of an identical degree of abstraction, rather than any others.
 We use Leave-One-Out (LOO) accuracy as the evaluation metric.
@@
                                   & MDP Level 0 & MDP Level 1 & MDP Level 2 \\ \hline
-\multicolumn{1}{|l|}{NLP Level 0} & 0.0 \%      & 0.0\%       & 0.0\%       \\ \hline
-\multicolumn{1}{|l|}{NLP Level 1} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
-\multicolumn{1}{|l|}{NLP Level 2} & 0.0\%       & 0.0\%       & 0.0\%       \\ \hline
+\multicolumn{1}{|l|}{NLP Level 0} & 36.7 \%      & 0.0\%       & \textbf{40.0\%}       \\ \hline
+\multicolumn{1}{|l|}{NLP Level 1} & 10.7\%       & 3.57 \%     & 14.3\%       \\ \hline
+\multicolumn{1}{|l|}{NLP Level 2} & \textbf{46.7\%}       & \textbf{26.7}\%       & 10.0\%       \\ \hline
 \end{tabular}
@@
 
+Contrary to what we predicted, the grounding accuracies obtained when the levels of natural language and MDP match were not the most prominent at any layer of abstraction.
+Examining our results more closely, we find that there are some interesting properties of the abstraction that are captured in the results.
+Over the course of the subsequent error analysis, one universal problem present in our experiments is data sparsity; each experiment was conducted using only 30 samples (whereas the original experiments conducted by MacGlashan et.al.
+utilized more than 100 samples).
+
+We first notice that our worst result comes from using low-level language at the mid-level MDP; in the entire CleanupWorld AMDP, the jump in abstraction between levels is largest between the low and mid levels so the difficulty in grounding success when mixing between these levels is predictably difficult.
+Additionally, notice how low-level language commands like ``walk three steps south'' correspond to moving through a single door and entering a room (at the mid-level).
+Logically, it is harder to establish the translation between the given natural language and two, distinct actions; this fact becomes even more apparent when considering the accuracy when grounding low-level language to the high-level MDP.
+Since language commands like the previous example ground to a single ``move to rooom'' action in the high-level MDP, it makes sense that these groundings were successful.
+
+Returning to the notion of gap between layers of abstraction, we note that this gap is minimal between the mid and high levels of the AMDP which is reflected in our (relatively) high accuracies for both groundings involving these two levels exclusively.
+When examining the overall success of grounding in the low-level MDP, we recognize that the overall vocabulary of high-level commands is much smaller than that of low-level commands which, coupled with our data sparsity issues, make the IBM Model II translation more reliable at the higher level.
+We posit that the accuracy for low-level language groundings in the low-level MDP would be much higher provided a larger number of data samples.
 \section{Conclusion and Future Work}
@@
 
-Lorem ipsum
+In this work, we analyzed AMDPs as a new, alternative framework for hierarchically decomposing large, intractable tasks into multiple layers with varying degress of abstraction.
+The goal of our analysis was to verify the strength and reliability of the proposed AMDP abstractions by examining the success of grounding natural language with varying degress of abstraction to reward functions in each layer of the AMDP.
+While our results do not support our initial hypothesis, it is clear that properties of the abstraction between layers of the AMDP are visible in the collected experimental results.
+Additionally, it is worth noting that all of our experiments were conducted using a very small amount of data in comparison to those of the original grounding reward functions work.
+We believe that more effort should be allocated towards data collection in order to definitively accept/reject our proposed hypothesis before continuing onwards to the more interesting and challenging problem of learning the layers of the AMDP given only the base-level MDP as input.
 

### 2016-05-10 src/commands/amdp/experiments/CleanupAMDPExperiment.java

@@ -6,7 +6,10 @@ import commands.amdp.experiments.cleanupL2.CleanupL2ControllerConstructor;
 import commands.amdp.replicate.mt.IBM2;
 import commands.data.TrainingElement;
 import commands.model3.TaskModule;
+import commands.model3.mt.Tokenizer;
+import commands.model3.weaklysupervisedinterface.MTWeaklySupervisedModel;
 import commands.model3.weaklysupervisedinterface.WeaklySupervisedController;
+import commands.model3.weaklysupervisedinterface.WeaklySupervisedLanguageModel;
 import generativemodel.GMQueryResult;
 import generativemodel.GenerativeModel;
 
@@ -26,6 +29,11 @@ public class CleanupAMDPExperiment {
 
     public static void createAndAddLanguageModel(WeaklySupervisedController controller){
         IBM2 model = new IBM2();
+//        Tokenizer tokenizer = new Tokenizer(true, true);
+//        tokenizer.addDelimiter("-");
+//
+//        WeaklySupervisedLanguageModel model = new MTWeaklySupervisedModel(controller, tokenizer, 10);
+
         //set our controller to use the MT model we created
         controller.setLanguageModel(model);
     }
@@ -139,8 +147,8 @@ public class CleanupAMDPExperiment {
          * L2-L1 = 0.143 (only 28 samples?)
          */
 
-//        boolean cacheIRLResults = true;
-        boolean cacheIRLResults = false;
+        boolean cacheIRLResults = true;
+//        boolean cacheIRLResults = false;
 
         CleanupL0ControllerConstructor l0Controller = new CleanupL0ControllerConstructor();
         CleanupL1ControllerConstructor l1Controller = new CleanupL1ControllerConstructor();
@@ -153,11 +161,11 @@ public class CleanupAMDPExperiment {
 //            cacheIRLResultsFor(l2Controller, l2Controller.EXPERTDATASET, L2_TRAJ_CACHE);
         }
 
-//        LOOTest(l0Controller, l0Controller.EXPERTDATASET, L0_TRAJ_CACHE); //L0
+        LOOTest(l0Controller, l0Controller.EXPERTDATASET, "data/jerryTrajectoryCache"); //L0
[…]

### 2016-05-10 paper/paper-template-latex/paper_template.tex
Fixed spelling

@@
 Our goal in this work is to analyze an alternative method of abstraction for sequential decision making problems that utilizes multiple layers of abstraction over all components of the Markov Decision Process (MDP) in order to efficiently learn in complex domains.
-In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the succeess of the grounding process as a measure of the strength of the abstraction.
+In order to convey the strength of the abstraction imposed by the abstract Markov decision process (AMDP) formalism, we extend prior work on grounding natural language commands to reward functions and, in particular, evaluate the success of the grounding process as a measure of the strength of the abstraction.
 
